M-M paper, morphological bias

### 2015-03-23 papers/MbhMsph/mm.tex
mon

Some studies reported a slope steeper than 1,  

@@

and reported a slope of $0.75 \pm 0.10$ for their $M_{\rm BH} - L_{\rm sph}$ relation. 

@@

which can be described by a single power-law $M_{\rm BH} \propto \sigma^5$ 

@@

That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than single, power-law, 

@@

miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 

@@

it should be noted that $\sim$ $20\%$ of ``core galaxies'' are not core-S\'ersic spheroids 

@@

where the black hole and the bulge grow in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 

@@

for the S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
(spheroid stellar mass) diagrams, respectively.

@@

and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies.
\\

range mbh not to miss the bend

\section{Data}
\label{sec:data}
\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}

>>>>

Some studies reported a slope steeper than one,  

@@

and reported a slope below unity for their $M_{\rm BH} - M_{\rm sph}$ relation. 

@@

which can be described by a single power-law ($M_{\rm BH} \propto \sigma^5$) 

@@

That is, the $M_{\rm BH} - L_{\rm sph}$ relation should be better described by a ``broken'', rather than a single, power-law, 

@@

can easily miss the change in slope occuring at $M_{\rm BH} \approx 10^{(8 \pm 1)}\rm~M_\odot$, 

@@

it should be noted that $\sim$20\% of ``core galaxies'' are not core-S\'ersic spheroids 

@@

where the black hole and the bulge grow at the same pace, increasing their mass in lock steps ($M_{\rm BH} \propto L_{\rm sph}^1$), 

@@

for S\'ersic/core-S\'ersic spheroids in the $M_{\rm BH} - L_{\rm sph}$ and $M_{\rm BH} - M_{\rm *,sph}$ 
(spheroid stellar mass) diagrams, respectively, probing down to $M_{\rm BH} \approx 10^6\rm~M_\odot$. 

@@

and $\sim$80\% of their S\'ersic spheroids were morphologically classified as bulges of disk galaxies (lenticulars and spirals). \\
Several recent papers \citep{jiang2011a,jiang2013,mathur2012,reines2013} claimed an offset at the low-mass end of the $M_{\rm BH} - M_{\rm *,sph}$ diagram,
such that the black hole mass is lower than expected from the near-linear correlation traced by the high-mass, early-type spheroids. 
However, \cite{grahamscott2015} showed that the low-mass spheroids ($10^{8.5} \lesssim M_{\rm *,sph}/{\rm M_\odot} \lesssim 10^{10.5}$) 
are not randomly offset from the high-mass, near-linear correlation, 
but lie on the two times steeper relation traced by the S\'ersic spheroids. \\
here: 66 galaxies, largest dataset to date
status-of-the-art decomp.
3.6 um best tracer of stellar mass
9 systems w $M_{\rm BH} \lesssim 10^7\rm~M_\odot$
17 spirals

\section{Data}
\label{sec:data}

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/mag_lit_vs_mag_my.pdf}
\caption{}
\label{fig:}
\end{center}
\end{figure}
